Unreliable heterogeneity: how measurement error obscures heterogeneity in meta-analyses in psychology

### 2023-06-18 manuscript/unreliable-heterogeneity-manuscript.qmd
fixed figure 3 width

```{r Figure 3, echo=FALSE, out.width = '90%'}
#| fig.env: figure*
#| fig-pos: 't'
#| fig-cap: "Unreliability in primary studies typically leads to a net negative bias even for small degrees of heterogeneity. Effect size is Pearson’s r and rows indicate the number of studies in the meta-analysis. The x-axis indicates average effect size and the y-axis estimated heterogeneity in standard deviations averaged across 10,000 replications. Columns indicate the nominal true heterogeneity standard deviation $\tau$. Due to effect size truncation in Pearson’s r these values may differ from actual true heterogeneity standard deviation (black solid lines). Each dashed line corresponds to an average reliability in primary studies. Results are for standard deviation in reliability = 0.15, within-study sample size = 150. Code to reproduce figure: osf.io/8ygwj."

>>>>

```{r Figure 3, echo=FALSE, out.width = '100%'}
#| fig.env: figure*
#| fig-pos: 't'
#| fig-cap: "Unreliability in primary studies typically leads to a net negative bias even for small degrees of heterogeneity. Effect size is Pearson’s r and rows indicate the number of studies in the meta-analysis. The x-axis indicates average effect size and the y-axis estimated heterogeneity in standard deviations averaged across 10,000 replications. Columns indicate the nominal true heterogeneity standard deviation $\tau$. Due to effect size truncation in Pearson’s r these values may differ from actual true heterogeneity standard deviation (black solid lines). Each dashed line corresponds to an average reliability in primary studies. Results are for standard deviation in reliability = 0.15, within-study sample size = 150. Code to reproduce figure: osf.io/8ygwj."
